The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
hab sel fst scale para

Habitat selection - can be measured by RSFs and importance of scale:

*  Johnson (1980) identified four orders of habitat selection: (1) the geographical range of a species, (2) the home range of an individual, (3) the habitat patches within the home range and (4) specific resources within a habitat patch.

>>>>

Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales. Habitat selection is often
measured using resource selection functions (RSFs) and species distribution
models (SDMs). Both of these methods are based on the proportion of used
resources and available resources for an animal. Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, (3) the habitat patches within the home range and
(4) specific resources within a habitat patch. Extending beyond this
hierarchical perspective, Mayor (2009) reviewed scale in habitat selection and

Habitat selection - can be measured by RSFs and importance of scale: 
Scale in habitat selection... Mayor (2019)

Habitat selection is scale dependent and 
*  Johnson (1980)
